Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2015-06-08 version1.0/HBM.tex
a couple more small corrections
ruth's changes

For our calibration of \rhostar-$F_8$, we used a sample of Kepler stars with
both asteroseismic and flicker measurements available. \citet{chaplin:2014}
report asteroseismic \rhostar\ estimates (and the associated uncertainties) for
518 Kepler stars. The authors report three different sets of results, depending
on the choice of \Teff\ and \FeH, and in this work we elected to use values
reported in their Table 6 over Table 5, and Table 5 over Table 4. We
additionally used the 71 additional planet hosting stars with asteroseismology
reported in \citet{huber:2013} but not reported in \citet{chaplin:2014}. Values
for flicker and range were taken from \citet{kipping:2014}, based upon the
methods described in \citet{bastien:2013}. Following \citet{kipping:2014} and
for reasons described there-in, we only include targets in our calibration for
which:

@@

We use the same sample for our calibration of \logg, except that we exclude the
\citet{huber:2013} data, since these authors do not provide estimates of
\logg\footnote{Whilst we could compute \logg\ ourselves from the reported
masses and radii, this could only be done under the incorrect assumption of
zero covariance between $M_{\star}$ and $R_{\star}$.}

@@

We model the stochastic relationship between $F_8$, \logg\ and \rhostar,
accounting for the fact that there exists some intrinsic scatter in
the dependent variable, and including the heteroskedastic uncertainties on both
the dependent and independent variables.
There are two excellent reasons for modelling the relation stochastically;
firstly, if the intrinsic scatter is ignored and the relation between
variables is assumed to be deterministic, those data points with smaller
measurement uncertainties may have an unrepresentative greater weighting
during the fitting process.
Secondly, we are interested in producing probability distributions over stellar
densities and surface gravities, as opposed to point estimates, and propagating
these probability distributions through to subsequent analyses.
Several recent studies have required posterior Probability Distribution
Function (PDF) samples, in order to conduct their (hierarchical)
analyses \citep[e.g.][]{rogers:2015, foreman-mackey:2014, angus:2015}.

@@

The two models describing the relationship between $F_8$, \logg and \rhostar
density can be written as
\begin{equation}
	\log_{10}(\rho_\star) \sim \mathcal{N}(\mu = \alpha + \beta
	\log_{10}(F_8), \sigma = \sigma_{\rho}),
\end{equation}
\label{eq:rho}
and
\begin{equation}
	\log_{10}(g) \sim \mathcal{N}(\mu = \gamma + \delta \log_{10}(F_8),
	\sigma = \sigma_g)
\end{equation}
\label{eq:logg}
The free parameters of the two models are $\alpha$, $\beta$, $\sigma_{\rho}$,
$\gamma$, $\delta$, and $\sigma_g$.
These relationships can be described as Gaussian distributions with means
given by the equation of a straight line, and standard deviations which
describe the intrinsic scatter about the mean.

In order to account for the two-dimensional observational uncertainties in
this data set, we marginalize over the latent, `true' values of $F_8$,
\rhostar and \logg using the importance sampling method of
\citep{hogg:2010}\footnote{Note that while the pseudo-marginal MCMC method of
\citep{andrieu:2009} provides a truly unbiased estimate of the marginalized
likelhood, we expect any bias introduced by the importance sampling method to
be negligable.}.
The observed values of the variables; $F_8$, \rhostar and \logg can be thought
of as a single `draw' from an underlying (assumed Gaussian) probability
distribution, with mean equal to the `true' value\footnote{We use `true' to
mean the value that would have been observed, given infinitely high
signal-to-noise.} and standard deviation equal to the observational
uncertainty.
We compute the likelihood of the data given the model, marginalized over the
true values, using importance sampling.
We sample from the posterior PDFs of the true values of the variables,
conditioned on the observed values, and compute the likelihood of each of those
samples.
% These posterior PDFs could be produced by the astronomers who provide the
% catalog.
% If posterior samples are made available, they can be used in this stage of
% the inference.
% In the event that they are not provided however, they can be generated.
% For example, the $log(g)$ values used here are point estimates of the
% posterior PDFs of $log(g)$, produced by \citet{chaplin:2014} using
% {\it Kepler} light curves and stellar models.
We would use the posterior samples generated in previous model fitting process
if they were available, however generating new samples is an acceptable
approximation provided the posteriors are Gaussian (or log-Normal) and the
priors used by the previous fitters were uninformative.
Such an approximation {\it will not be necessary} for those studies using
\rhostar or \logg calculated using the newly-calibrated relations
presented here, as long as the posterior samples are published.
After producing new posterior PDF samples we then add up the individual
log-likelihoods of each sample to compute the total marginalized likelihood
for a star.
The marginalized likelihood of the whole dataset is then computed as the sum
of the log-likelihoods of each star.
The importance sampling method allows us to approximate the integral over the
latent variables.

>>>>

For our calibration data, we used a sample of \Kepler\ stars with
both asteroseismic and flicker measurements available. \citet{chaplin:2014}
report asteroseismic \rhostar\ estimates (and the associated uncertainties) for
518 \Kepler\ stars. The authors report three different sets of results, 
depending on the choice of \Teff\ and \FeH, and in this work we elected to use 
values reported in their Table 6 over Table 5, and Table 5 over Table 4. We
additionally used the 71 additional planet hosting stars with asteroseismology
reported in \citet{huber:2013} but not reported in \citet{chaplin:2014}. Values
for flicker and ``range'' were taken from \citet{kipping:2014}, based upon the
methods described in \citet{bastien:2013}. Following \citet{kipping:2014} and
for reasons described there-in, we only include targets in our calibration for
which:

@@

We use the same sample for our calibration of \logg, except that we exclude the
\citet{huber:2013} data, since these authors do not provide estimates of
\logg\footnote{Whilst we could compute \logg\ ourselves from the reported
masses and radii, this could only be done under the incorrect assumption of
zero covariance between $M_{\star}$ and $R_{\star}$.}.

@@

We model the stochastic relationship between $F_8$ and \logg\ or \rhostar,
accounting for the fact that there exists some intrinsic scatter in
the dependent variable, and including the heteroskedastic uncertainties on both
the dependent and independent variables.
There are two excellent reasons for modelling the relation stochastically;
firstly, if the intrinsic scatter is ignored and the relation between
variables is assumed to be deterministic, those data points with smaller
measurement uncertainties may have an unrepresentative greater weighting
during the fitting process.
Secondly, we are interested in producing probability distributions over stellar
densities and surface gravities, as opposed to point estimates, and propagating
these probability distributions through to subsequent analyses.
Several recent studies have required posterior Probability Distribution
Function (PDF) samples, in order to conduct their (hierarchical)
analyses \citep[e.g.][]{rogers:2015, foreman-mackey:2014, angus:2015}.

@@

The two models describing the relationship between $F_8$, \logg\ and \rhostar\
density can be written as
\begin{equation}
	\log_{10}(\rho_\star) \sim \mathcal{N}(\mu = \alpha + \beta
	\log_{10}(F_8), \sigma = \sigma_{\rho}),
\end{equation}
\label{eq:rho}
and
\begin{equation}
	\log_{10}(g) \sim \mathcal{N}(\mu = \gamma + \delta \log_{10}(F_8),
	\sigma = \sigma_g)
\end{equation}
\label{eq:logg}
The free parameters of the two models are $\alpha$, $\beta$, $\sigma_{\rho}$,
$\gamma$, $\delta$, and $\sigma_g$.
These relationships can be described as Gaussian distributions with means
given by the equation of a straight line, and standard deviations which
describe the intrinsic scatter about the mean.

In order to account for the two-dimensional observational uncertainties in
this data set, we marginalize over the latent, `true' values of $F_8$,
\rhostar\ and \logg\ using the importance sampling method of
\citep{hogg:2010}\footnote{Note that while the pseudo-marginal MCMC method of
\citep{andrieu:2009} provides a truly unbiased estimate of the marginalized
likelhood, we expect any bias introduced by the importance sampling method to
be negligable.}.
In what follows we give an overview of this procedure, but encourage the reader
to refer back  to this original reference for a more detailed description of
the mathematics.
The observed values of the variables; $F_8$, \rhostar\ and \logg\ can be thought
of as a single `draw' from an underlying (assumed Gaussian) probability
distribution, with mean equal to the `true' value\footnote{We use `true' to
mean the value that would have been observed, given infinitely high
signal-to-noise.} and standard deviation equal to the observational
uncertainty.
We compute the likelihood of the data given the model, marginalized over the
true values, using importance sampling.
We sample from the posterior PDFs of the true values of the variables,
conditioned on the observed values, and compute the likelihood of each of those
samples.
% These posterior PDFs could be produced by the astronomers who provide the
% catalog.
% If posterior samples are made available, they can be used in this stage of
% the inference.
% In the event that they are not provided however, they can be generated.
% For example, the $log(g)$ values used here are point estimates of the
% posterior PDFs of $log(g)$, produced by \citet{chaplin:2014} using
% {\it Kepler} light curves and stellar models.
We would use the posterior samples generated in previous model fitting process
if they were available, however generating new samples is an acceptable
approximation provided the posteriors are Gaussian (or log-Normal) and the
priors used by the previous fitters were uninformative.
Such an approximation {\it will not be necessary} for those studies using
\rhostar\ or \logg\ calculated using the newly-calibrated relations
presented here, as long as the posterior samples are published.
After producing new posterior PDF samples we then add up the individual
log-likelihoods of each sample to compute the total marginalized likelihood
for a star.
The marginalized likelihood of the whole dataset is then computed as the sum
of the log-likelihoods of each star.
The importance sampling method allows us to approximate the integral over the
latent variables.

### 2015-06-08 version1.0/introduction.tex
ruth's changes

% Stellar characterization techniaues overview, traditionally frequentist

% who cares about characterization?

@@

Basic stellar parameters, such as effective temperature and surface gravity, 
can be inferred using one (or more) of several types of observations, e.g. 
spectroscopy, photometry, interferometry, etc. This inference can be done by
invoking theoretical models or by building an empirical calibration library.
As an example, an observed stellar spectrum could be matched against a library of 
theoretical spectra generated using stellar atmosphere models, or, against a 
library of observed spectra of ``standard stars'', serving as calibrators.
%Fundamental stellar parameters, such as mass and radius, which cannot be 
%directly inferred from the available observations can often be inferred by 
%invoking theoretical stellar models, e.g. fitting model isochrones to 
%spectroscopic measurements.
Regardless of the approach, be it theoretical or empirical, the methods used
for the inference of stellar parameters are traditionally ``deterministic''.
In this context, a deterministic model can be loosely described as one where
a particular observational input always returns a single-valued output for a 
parameter of interest. In this framework, nature itself has no variance and
our underlying model is considered to be a perfect description of reality.

An alternative approach for inferring model parameters is the 
``probabilistic'' one. Unlike the deterministic case, a single observational 
input is intepretted to be caused by a range of possible model parameters
described by a probability distribution. This statement is true even in the case
of a perfect observation of infinite signal-to-noise, since our underlying 
model itself comes with uncertainty. In recent years, there has been a shift 
towards such methods in several areas of astronomy, particularly within the 
exoplanet community. For example, \citet{wolfgang:2015} considered that
the mass-radius relationship of exoplanets is probabilistic, since a particular
sized planet could be due to a range of planet masses, thanks to variances in
compositions, environment and other circumstances. These recent demonstrations
in exoplanetary science have prompted us to consider the need for treating the 
parent stars in the same probabilistic framework, with potential applications 
spanning many fields of astronomy.

The demand for probilistic stellar parameters is not only motivated by the fact
that probability distributions are far more representative of our `beliefs'
about astrophysical parameters, but also... (ruth will continue this sentence)

@@

>>>>

@@

Basic stellar parameters, such as effective temperature and surface gravity, 
can be inferred using one (or more) of several types of observations, such as
spectroscopy, photometry, interferometry, etc. This inference can be done by
invoking theoretical models or by building an empirical calibration library.
For example, an observed stellar spectrum could be matched against a library of 
theoretical spectra generated using stellar atmosphere models, or, against a 
library of observed spectra of ``standard stars'', serving as calibrators.
%Fundamental stellar parameters, such as mass and radius, which cannot be 
%directly inferred from the available observations can often be inferred by 
%invoking theoretical stellar models, e.g. fitting model isochrones to 
%spectroscopic measurements.
Regardless of the approach, be it theoretical or empirical, the methods used
for the inference of stellar parameters are traditionally ``deterministic''.
In this context, a deterministic model can be loosely described as one where
a particular observational input always returns a single-valued output for a 
parameter of interest. In this framework, nature itself has no variance and
our underlying model is considered to be a perfect description of reality.

An alternative approach for inferring model parameters is the 
``probabilistic'' one. Unlike the deterministic case, a single observational 
input is intepretted to be caused by a range of possible model parameters
described by a probability distribution. This statement is true even in the case
of a perfect observation of infinite signal-to-noise, since our underlying 
model itself comes with uncertainty. In recent years, there has been a shift 
towards such methods in several areas of astronomy, particularly within the 
exoplanet community. For example, \citet{wolfgang:2015} considered that
the mass-radius relationship of exoplanets is probabilistic, since a particular
sized planet could be due to a range of planet masses, cdue to unmodeled 
variances in compositions, environment and other complications. These recent 
demonstrations in exoplanetary science have prompted us to consider the need for 
treating the parent stars in the same probabilistic framework, with potential 
applications spanning many fields of astronomy.

\textbf{
The demand for probilistic stellar parameters is not only motivated by the fact
that probability distributions are far more representative of our `beliefs'
about astrophysical parameters, but also... (ruth will continue this sentence)
}

@@

% RA text...

One of the more recent tools developed to characterize stars is known as
``flicker'' \citep{bastien:2013}. Flicker is a proxy for the scatter on an
8-hour timescale (denoted as $F_8$) in a broad visible bandpass time series
photometric light curve, such as that from \textit{Kepler} or the upcoming TESS
mission. A more detailed account of the proceedure to calculate flicker is
described in \citet{bastien:2013}. As shown in \citet{bastien:2013}, flicker
displays a remarkable correlation to the asteroseismically determined parent
star surface gravities (\logg). Turning this around, the observation implies
that flicker can be used to blindly infer surface gravities at the level of
$\sim0.1$\,dex, an attractive proposition given the wealth of photometric light
curves available through the array of exoplanet transit missions flying and
scheduled to launch.

\citet{cranmer:2014} demonstrated that models of stellar surface granulation are 
indeed reproduce a flicker effect in close agreement with that observed by
\citet{bastien:2013}, providing a physically-plausible explanation. Since
surface gravity is highly correlated to mean stellar density (\rhostar) on
evolutionary tracks, \citet{kipping:2014} showed that flicker can be also
be used to infer \rhostar, which is more useful for exoplanet transit
analysis \citep{seager:2003}.

Whether one calibrates flicker to \logg\ or \rhostar, there are several aspects
of the problem which are attractive for our purposes of a simple demonstration
of probabilistic inference of stellar parameters. Firstly, in log-log space the
relationship is very simple, appearing to be linear \citep{kipping:2014}. 
Secondly, there is a sufficiently large number of points in the sample (439 
stars) to constrain a population-based model. Thirdly, there is significant 
excess scatter around the best-fitting relation implying that a deterministic 
model is inadequate. This is not surprising given that granulation is a complex 
and messy process for which one should not expect any parametric model to 
provide a perfect description. For these reasons, we identify the calibration of 
flicker to \logg\ and \rhostar\ as a well-posed problem to first demonstrate 
probabilistic inference in the arena of stellar characterization.

### 2015-06-08 version1.0/manuscript.tex
adding text
ruth's changes

%% Authors
\author{
	{\bf	R.~Angus\altaffilmark{1,2},
		D.~M.~Kipping\altaffilmark{2,3},
	}
}

@@

% aims
The relations between observable stellar parameters are usually assumed to be
deterministic.
That is, given an infinitely precise measurement of independant
variable, `$x$', and some model, the value of dependant variable, `y' can be
known exactly.
In practise this assumption is rarely valid and intrinsic stochasticity means
that two stars with exactly the same `$x$', will have slightly different
`$y$`s.
% methods
The relation between short-timescale brightness fluctuations (flicker) of stars
and both surface gravity \citep{bastien:2013} and stellar density
\citep{kipping:2014} are two such stochastic relations that have, until now,
been treated as deterministic ones.
We recalibrate these relations in a probabilistic framework, using
Hierarchical Bayesian Modelling (HBM) and constrain the instrinsic scatter in
the relations.
Our treatment also fully accounts for the observational uncertainties on all
variables.
% results
These new relations provide probability distributions over values of $\log(g)$
or \rhostar for given measurements of flicker.
Such probability distributions will be useful for subsequent studies using
probabilistic inference.

@@

One of the more recent tools developed to characterize stars is known as
``flicker'' \citep{bastien:2013}. Flicker is a proxy for the scatter on an
8-hour timescale (dubbed $F_8$) in a broad visible bandpass time series
photometric light curve, such as that from \textit{Kepler} or the upcoming TESS
mission. A more detailed account of the proceedure to calculate flicker is
described in \citet{bastien:2013}. As shown in \citet{bastien:2013}, flicker
displays a remarkable correlation to the asteroseismically determined parent
star surface gravities (\logg). Turning this around, the observation implies
that flicker can be used to blindly infer surface gravities at the level of
$\sim0.1$\,dex, an attractive proposition given the wealth of photometric light
curves available through the array of exoplanet transit missions flying and
scheduled to launch.

\citet{cranmer:2014} demonstrated that stellar surface granulation is expected
to reproduce a flicker effect in close agreement with that observed by
\citet{bastien:2013}, providing a physically-plausible explanation. Since
surface gravity is highly correlated to mean stellar density (\rhostar) on
evolutionary tracks, \citet{kipping:2014} showed that flicker can be also
be used to infer \rhostar, which is more useful for exoplanet transit
analysis.

Whether one calibrates flicker to \logg\ or \rhostar, there are several aspects
of the problem which are attractive for our purposes of a simple demonstration
of probabilistic inference of stellar parameters. Firstly, in log-log space the
relationship is very simple, appearing to be linear. Secondly, there is a
sufficiently number of points in the sample (439 stars) to constrain a
population-based model. Thirdly, there is significant excess scatter around the
best-fitting relation implying that a deterministic model is inadequate. This is
not surprising given that granulation is a complex and messy process for which
one should not expect any parametric model to provide a perfect description. For
these reasons, we identify the calibration of flicker to \logg\ and \rhostar\
as a well-posed problem to first demonstrate probabilistic inference in the
arena of stellar characterization.

@@

\section{APPLICATION}
\label{sec:appication}

\input{application.tex}

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}

>>>>

%% Authors
\author{
	{\bf	Ruth~Angus\altaffilmark{1,2},
		David.~M.~Kipping\altaffilmark{2,3},
	}
}

@@

% aims
The relations between observable stellar parameters are usually assumed to be
deterministic.
That is, given an infinitely precise measurement of independant
variable, `$x$', and some model, the value of dependant variable, `y' can be
known exactly.
In practise this assumption is rarely valid and intrinsic stochasticity means
that two stars with exactly the same `$x$', will have slightly different
`$y$`s.
% methods
The relation between short-timescale brightness fluctuations (flicker) of stars
and both surface gravity \citep{bastien:2013} and stellar density
\citep{kipping:2014} are two such stochastic relations that have, until now,
been treated as deterministic ones.
We recalibrate these relations in a probabilistic framework, using
Hierarchical Bayesian Modelling (HBM) and constrain the instrinsic scatter in
the relations.
Our treatment also fully accounts for the observational uncertainties on all
variables.
% results
These new relations provide probability distributions over values of \logg\
or \rhostar\ for given measurements of flicker.
Such probability distributions will be useful for subsequent studies using
probabilistic inference.

@@

@@

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]{seager:2003} 
Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}
